\begin{entrylist}


    \entry
    {
        11/23 -- today \\\footnotesize{Engineer III \\ (Security),\\ then Senior Engineer \\ (Payments)}        \\
    }
    {Senior Backend Software Engineer}
    {\href{https://monzo.com}{Monzo Bank}}
    {
        Worked both on Payments as building \textbf{products} for retail customers, and in Security in an \textbf{SRE}-heavy role with wide scope.

        \para

        Owned secret-management, public-key infrastructure, and preventive and detective security controls (eg. around \textbf{intrusion, exfiltration, DDoS}, etc).

        \para

        Maintained critical zero-downtime infrastructure such as \textbf{Kubernetes}, \textbf{cloud networking}, and \textbf{sensitive key material} management.
    }
    \entry
    {
        06/20 -- 11/23   \\\footnotesize{part-time,\\ then Engineer,\\ then Senior Engineer}        \\
    }
    {Senior Backend Software Engineer}
    {\href{https://blockchain.com/about}{Blockchain.com}}
    {
        Owned several \textbf{JVM} (mainly \textbf{Kotlin}) real-time financial services critical for business operation and central to
        to user experience and transaction auditing; like ledger-keeping/accounting and indicative pricing.

        \para
        Designed and scaled up \textbf{stateful distributed} systems with an event-driven architecture.

        \para
        Reviewed systems' architecture designs and software development methods to cultivate \textbf{sustainable engineering practices}
        and achieve \textbf{operational excellence} within the wider company.

%    \para
%    Implementing application \textbf{performance monitoring} and performing \textbf{production incident response}.

%    \para
%    \textbf{Interviewing and onboarding new engineers} in the team to the complex product and architecture of Blockchain.

%    \para
%    \textbf{Engineering tooling} to facilitate development, improve build processes, and enhance observability.
    }
    \entry
    {06/19 --        \\ 10/19        \\\footnotesize{intern}}
    {Software Engineer}
    {Emit, Inc.}
    {
        Four-person startup with its own smartwatch aiming to provide time-analytics to
        institutional customers.

        \para
        Provided real-time insights on customer data by developing data processing pipelines and libraries in
        \textbf{Kotlin} and \textbf{Python} on top of serverless tech on \textbf{AWS (Lambda,
            DynamoDB, ElasticSearch)}.
    }
\end{entrylist}
